\includegraphics*[width=0.4\textwidth]{hpi_logo_2017.eps}\\ \vspace{24pt} Genetic Doodle Jump

### 2018-03-29 paper/paper.tex
user interface intro

\subsection{Simplified implementation}

@@

>>>>

\subsection{Simplified implementation}
\label{sec:si}

@@

To start the genetic algorithm and inform about the current learning progress we implemented a user interface (UI). For that, we used the simplified Doodle Jump implementation as a fundamental (section \ref{sec:si}). Then some functionalities for the genetic algorithm had to be added. Fig. \ref{abb:ui} shows a screenshot of the UI which was taken after the game was played for 83 generations. The genetic algorithm currently is in the 84th generation. This is displayed in the top left corner. The

\begin{figure}[h]
\begin{center}
\includegraphics*[width=1\textwidth]{images/ui}\\
\caption{Screenshot of our UI}
\label{abb:ui}
\end{center}
\end{figure}
